MSB1015 Project

### 2024-10-18 Code/MSB1015-Project.Rmd
Update MSB1015-Project.Rmd
Removed the number of trees from the PCoA function call

# Call the function for the unsupervised random forest PCoA 
PCoA_plots_rawdata <- PCoA_proximity_plot(data, "tumor_stage", n_trees = 10)
grid.arrange(grobs = PCoA_plots_rawdata, ncol = 2)

>>>>

# Call the function for the unsupervised random forest PCoA 
PCoA_plots_rawdata <- PCoA_proximity_plot(data, "tumor_stage")
grid.arrange(grobs = PCoA_plots_rawdata, ncol = 2)
